\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{fontawesome}
\usepackage{pifont}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Lucas Duport}
\end{center}

\begin{center}
\small \faPhone\ +33 6 87 61 33 64 $|$
\faEnvelope\ \href{mailto:cv.lucasduport@icloud.com}{cv.lucasduport@icloud.com} $|$
\faLink\ \href{https://lucasduport.cc}{lucasduport.cc}
\small 

\end{center}

\begin{center}
\small \faCalendar\ Internship in February 2026 (6 months) $|$
\faGlobe\ Worldwide
\end{center}

%-----------EDUCATION-----------
\section*{ \small \faGraduationCap\ \large Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {EPITA - Master’s Degree in Computer Engineering}{Paris, France}
      {Major: Artificial Intelligence \& Computer Vision | GPA: 3.7 |  Member of student association}{2021 -- 2026}
      
\resumeSubheading
  {San Francisco State University - Computer Science}{San Francisco, CA}
  {Exchange Semester | GPA: 3.9 | \textit{EPITA Student Ambassador}}{2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section*{ \small  \faBriefcase\ \large Experience}  \resumeSubHeadingListStart
    \resumeSubheading
      {Teaching Assistant}{Paris, France}
      {EPITA}{2023 -- Present}
      \resumeItemListStart
        \resumeItem{Part of a team of 60 students that support 800+ third-year students in coding activities alongside my studies.}
        \resumeItem{Assisted in \textbf{debugging and answering technical questions} in various programming languages.}
        \resumeItem{Designed practicals and deployed automatic grading systems for 600+ first-year students.}
        \resumeItem{Attended workshops regarding pedagogic approach, posture, motivation, voice, and body language.}
        \resumeItem{Crash-tested multiple projects and test suites and gave constructive feedback.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Scientist Intern}{Grenoble, France}
      {STMicroelectronics}{2025 (6 months)}
      \resumeItemListStart
        \resumeItem{Developed a data augmentation pipeline using \textbf{RAG} for technical text summarization.}
        \resumeItem{Built a full-stack platform using FastAPI, with a frontend in HTML/CSS/JavaScript for data validation and annotation.}
        \resumeItem{Designed and improved a \textbf{root cause suggestion system} based on reported symptoms in collaboration with end-users.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{Paris, France}
      {Kerquest SAS}{2023 (2 months)}
      \resumeItemListStart
          \resumeItem{Developed a prototype computer vision system to \textbf{detect object types on a grid} in a production line, improving automation readiness.}
        \resumeItem{Created an operator-facing interface to assist with real-time detection and decision-making.}
        \resumeItem{Automated server installation using Debian Preseed, Ansible, and Bash scripts.}
      \resumeItemListEnd



  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section*{\small \faProjectDiagram\ \large Projects}
\resumeSubHeadingListStart

\resumeSubheading
  {TripAdvisor Review Analysis}{\small \faGroup\ \normalsize 5}
  {Python}{2025}
  \resumeItemListStart
    \resumeItem{Developed a pipeline to \textbf{classify hotel reviews and generate} synthetic text using keywords and ratings.}
    \resumeItem{Implemented and compared logistic regression, RNNs, FNNs, and transformers.}
  \resumeItemListEnd

\resumeSubheading
  {Sudoku OCR from Scratch}{\small \faGroup\ \normalsize 4}
  {C}{2023}
  \resumeItemListStart
    \resumeItem{Built an end-to-end system that \textbf{detects, extracts, and solves} Sudoku puzzles from images using classical 
    image processing and neural networks — entirely built in C without external libraries.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd
  
%-----------SKILLS & INTERESTS-----------
\section*{\small \faTools\ \large Skills \& Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Technical Skills}{: Python, C, C++, Java, SQL, JavaScript, Bash, C\#.} \\
    \textbf{Tools}{: Git/GitHub/GitLab, Docker, Linux.} \\
    \textbf{Languages}{: French (native), English (\textbf{970/990 TOEIC}), Italian (basic).} \\
    \textbf{Soft Skills}{: Curious, passionate, strong  communication, calm, positive, hard worker.} \\
    \textbf{Interests}{: Homelab, ski, watchmaking, poker, travel.}
  }}
\end{itemize}

%-----------REFERENCES-----------
\section*{\small \faUserTie\ \tiny References}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \textbf{Valentin SEUX}, Associate Director, Paris Site, EPITA \\
  \textit{valentin.seux@epita.fr} \\

  \item \textbf{Philippe VIALLETELLE}, Manufacturing Data Science, STMicroelectronics \\
  \textit{philippe.vialletelle@st.com} \\
\end{itemize}

\end{document}